\batcave: Calling somatic mutations with a tumor- and site-specific prior

### 2020-01-13 NAR_DRAFT.tex
fix plot and table
small fix to aucs in text

\subsection{Estimation of the mutation profile}
Many aspects of genomic architecture can affect the somatic mutation rate at multiple scales \cite{Buisson2019}.
Here we focus on a small-scale feature, the trinucleotide context, which is known to strongly affect the prior probability of single-nucleotide mutation \cite{Nik-Zainal2012a,Alexandrov2015,Lee-Six2018}.
The trinucleotide context of a genomic site consists of the identity of the reference base and the 3' and 5' flanking bases.
\rngcomment{There are six classes of base substitution: C$>$A, C$>$G, C$>$T, T$>$A, T$>$C, T$>$G (all referred to by the pyrimidine of the mutated Watson-Crick pair).
This results in a total of 32 ($4\times 2 \times 4$) reference contexts and 3 alternate bases per reference base.}
%Folding the central base to the pyrimidines, there are two possible bases at the focal site, and there are four possible bases 3' and 5' of the focal site, yielding $2 \cdot 4 \cdot 4$ possible tri-nucleotide contexts $C$.
%At the focal site, a mutation $m$ can be to any of three alternate alleles.
Indexing by the $c=\{1 \dots 32\}$ contexts and by the $m = \{1 \dots 3\}$ alternate bases, we have 96 possible substitution types $S_{m,c}$.
Eq.~\ref{eqn:full_prior} is then
\begin{equation}
  \label{eqn:detailed_prior}
  \mathrm{p}(\mathrm{S}_{m,c}) = \mathrm{p}(m \mid C = c) \mathrm{p}(C = c \mid M)\frac{\mathrm{p}(M)}{\mathrm{p}(C = c)}.
\end{equation}
The first two terms on the right-hand side can be estimated from the observed mutation profile (Fig.~\ref{NAR-realsigfig}).
%Here $\mathrm{p}(\mathrm{S}_{m,c})$ represents probability that a substitution of type $\mathrm{S}_{m,c}$ will occur.

@@

\subsection{Estimation of the mutation rate}
The final piece of Eq. \ref{eqn:detailed_prior} is $p(M)$, the prior probability of mutation, which we specify as the per-base per-division mutation rate $\mu$.
In an exponentially growing and neutrally evolving tumor, branching process calculations \cite{Williams2018} show that the expected total number of mutations $\mathrm{M_{tot}}$ between two allele frequencies ($f_{min}$,$f_{max}$) is
\begin{equation}
  \label{eqn:mut_rate}
  \mathrm{M_{tot}}(f_{min},f_{max}) = N\frac{\mu}{\beta}\left(\frac{1}{f_{min}} - \frac{1}{f_{max}}\right).
\end{equation}
The number of bases $N$ is $3\cdot10^9$ for a whole genome and $3\cdot10^7$ for a whole exome.
The quantity $\mu/\beta$ is the effective mutation rate, where $\beta$ is the fraction of cell divisions that lead to two surviving lineages.
We make the simplifying assumption that there is no cell death ($\beta = 1$), so we somewhat over-estimate $\mu$.
We then estimate $\mu$ by counting observed high-confidence mutations between allele frequencies $f_{min}$ and $f_{max}$.
\rngcomment{Sample contamination by normal cells can result in underestimation of tumor mutation allele frequencies.
To account for this, our implementation of BATCAVE takes as input an estimated sample purity $p_{ur}$.
All estimated allele frequencies are then multiplied by a factor of $1/p_{ur}$ before being used in Eq.~\ref{eqn:mut_rate}.}
We set $f_{max}$ to be the largest allele frequency in $\mathrm{D}$, but we must choose $f_{min}$ conservatively, depending on sequencing depth.
In the R implementation of \batcave, $f_{min}$ and $p_{ur}$ are free parameters.
For this paper, we set $f_{min} = 0.05$, because we are working at high depth.
For our simulated data analyses, we set $p_{ur}=1$, and for our real data analyses, we set $p_{ur}$ to the estimated purity.

@@

\rngcomment{
An assumption of the \batcave algorithm is that the mutation profile of low-confidence mutations is similar to that of the high-confidence mutations from which the prior is inferred.
To test this assumption, \texttt{batcaver} performs a statistical hypothesis test comparing these two mutation profiles \cite{Plunkett2019}.
If the two profiles differ at a significance threshold of $\alpha=0.05$, \texttt{batcaver} issues a warning and outputs the profiles.
%The user can then assess them and follow-up on any biologically interesting differences.
}

@@

\subsection{Real data}
We analyzed two real data sets, one from an acute myeloid leukemia (AML)~\cite{Griffith2015} and one from a multi-region sequencing experiment in breast cancer~\cite{Shi2018}.
We downloaded the normal and primary whole-genome AML tumor bam files from dbGaP accession number phs000159.v8.p4.
Griffith et al.\ generated a platinum set of variant calls for this tumor~\cite{Griffith2015}, which we used for our true positive dataset.
We downloaded the normal and tumor whole-exome breast cancer bam files from NCBI Sequence Read Archive accession SRP070662.
\rngcomment{Griffith et al.\ estimated the purity of their primary sample to be 90.7\%, and we used this value for tumor purity in \texttt{batcaver}.}
Shi et al.\ generated a gold set of variant calls for each tumor region sequenced~\cite{Shi2018}, which we used for our true positive dataset.
For these multi-region data, we analyzed the three biological replicates from each of six tumors (Table~\ref{table:01}), running \batcave separately on each of the eighteen samples, and we combined results to generate precision-recall curves.
\rngcomment{Shi et al.\ estimated sample purities of between 26\% and 80\%, and we used these estimates in \texttt{batcaver}.}
We called variants using Mutect 1.1.7 as in our simulations, except that both these data sets were originally aligned to GRCrh37, so we used that reference.

@@

\begin{table*}[b]
  \tableparts{%
  \caption{Variant calling metrics for all data sets.}
  \label{table:01}%
  }{%
  \begin{tabular}{lllllllllll}
  \toprule
  Scenario & Mutation profile & $\mu$ & \multicolumn{2}{c}{AUROC} & \multicolumn{2}{c}{AUPRC} & \multicolumn{2}{c}{ICI} 
  \\
  & & (estimated) & MuTect & \batcave & MuTect & \batcave & MuTect & \batcave
  \\
  \colrule
  100X whole genome & Concentrated & 3.6e-7 & .987 & .993 & .972 & .975 & .117 & .287
  \\
  100X whole genome & Intermediate & 3.2e-7 & .987 & .989 & .972 & .973 & .118 & .214
  \\
  100X whole genome & Diffuse & 3.2e-7 & .988 & .989 & .971 & .973 & .120 & .219
  \\
  500X whole exome & Concentrated & 3.6e-7 & .848 & .929 & .674 & .758 & .138 & .109
  \\
  500X whole exome & Intermediate & 3.6e-7 & .847 & .881 & .677 & .706 & .108 & .112 
  \\
  500X whole exome & Diffuse & 3.6e-7 & .850 & .873 & .676 & .698 & .105 & .116
  \\
  real AML \cite{Griffith2015} & Actual & 3.6e-8 & -- & -- & .988 & .996 & -- & --
  \\
  real breast \cite{Shi2018} & Actual & 6.6e-7 & -- & -- & .968 & .972 & -- & --
  \\
  \botrule
  \end{tabular}%
  }
  {$\mu$ = per-base mutation rate, AUROC/AUPRC = Area Under Receiver Operating Characteristic / Precision-Recall Curve, ICI = Integrated Calibration Index. Smaller values of ICI are superior.}
 \end{table*}

@@

Griffith et al.\ sequenced the whole genome of an acute myeloid leukemia (AML) primary tumor to a depth of $>$360X and used targeted sequencing to validate nearly 200,000 mutations~\cite{Griffith2015}.
We estimated a per-base mutation rate for this tumor of $3.6\times10^{-8}$, which is consistent with previous estimates of AML mutation rates \cite{Griffith2015,Williams2018}.
\rngcomment{
For this tumor, the mutation profiles of high- and low-confidence mutations differ ($p \sim 10^{-12}$).
The low-confidence mutation profile contains additional spikes of mutations corresponding to five substitution types (Fig.~\ref{fig:AML_profiles}).
}
Nevertheless, for both MuTect and \batcave, the precision-recall curve is almost perfect for the validated variants (.995 \& .996 area under the curve) (Fig.~\ref{NAR-wes_fig}E and Table~\ref{table:01}).

Shi et al.\ performed multi-region whole exome sequencing on six individual breast tumors to a mean target sequencing depth of 160X and validated all variants identified by three different variant calling pipelines~\cite{Shi2018}.
%We downloaded aligned reads for this tumor, and called variants with MuTect 1.1.7 as described in Materials \& Methods.
\rngcomment{Need to update!}
We estimated an average per-base mutation rate for these tumor regions of $6.6\times10^{-7}$, which is consistent with observed mutation rates for breast cancers \cite{Alexandrov2019} and with the low number of validated somatic mutations.
For the validated variants, MuTect and \batcave yielded almost identical precision-recall curves (Fig.~\ref{NAR-wes_fig}F and Table~\ref{table:01})

@@

\rngcomment{
Following MuTect \cite{Cibulskis2013}, \batcave assumes a uniform prior on the variant allele frequency.
In general, low-frequency variants are expected to be more common than high-frequency variants.
Nevertheless, the uniform frequency prior is appropriate when the goal is to make the best call possible at each potential variant site.
By favoring low-frequency and thus typically low-evidence variants, a nonuniform prior would increase the false positive rate.
Note however, that if the goal were not to best identify individual variants, but rather to best estimate the distribution of variant allele frequencies within the tumor, then a nonuniform frequency prior would be appropriate~\cite{Nielsen2012}.
}

\rngcomment{
To estimate the tumor mutation rate, \batcave uses a model of the distribution of variant allele frequencies  generated during exponential growth (Eq.~\ref{eqn:mut_rate}).
Mutations that change copy number might distort the empirical allele frequency distribution, biasing the estimate.
But substantially biasing the estimate would require copy number changes in a large number of genomic regions.
Nevertheless, a potential extension of the \batcave algorithm would be to incorporate external copy number calls in order to adjust allele frequencies before estimating the mutation rate.
}

\rngcomment{
Sequencing multiple regions of the same tumor is of growing interest for understanding tumor heterogeneity and evolution \cite{McGranahan2017}.
In fact, the breast cancer data we analyze came from a multi-region study~\cite{Shi2018}.
We called variants independently across samples, because MuTect only considers a single sample at a time.
But calling variants jointly across samples could substantially increase sensitivity.
In the future, the \batcave algorithm could be integrated into a multi-sample caller such as MultiSNV~\cite{Josephidou2015}.
In that case, an optimal implementation would likely exploit the relationship between mutational priors in related samples.
}

@@

An  implicit assumption of \batcave is that the mutational process does not change between high- and low-confidence variants, implying that the mutational profile of the tumor is temporally constant.
Recent studies have found differences in mutational profiles among variants of different allelic frequencies~\cite{Rubanova2018a}, and although in general those differences are relatively small, they can be significant in some cases.
\rngcomment{Our \texttt{batcaver} software warns the user if the high- and low-confidence mutational profiles are statistically different.
It also outputs those profiles, so the user can assess whether the difference will substantially affect their results.} 
A potential extension of the \batcave algorithm is to process potential variants in order of descending allelic frequency and to update the estimated mutational prior as the algorithm proceeds.
This approach might increase sensitivity to low-frequency variants generated by recently-arisen mutational processes, at the cost of potentially increasing sensitivity to patterns of sequencing error.

@@

\begin{table*}[b]
  \tableparts{%
  \caption{Sample summary for Shi et al. (2018)}
  \label{table:01}%
  }{%
  \begin{tabular}{lll}
  \toprule
  Sample & Purity estimate (\%) & Mutation rate estimate 
  \\
  \colrule
  Case 1 biorep A & 53.8 & 9.3e-7 
  \\
  Case 1 biorep B & 46.3 & 8.4e-7 
  \\
  Case 1 biorep C & 26.0 & 1.0e-6 
  \\
  Case 2 biorep A & 40.0 & 1.1e-6 
  \\
  Case 2 biorep B & 32.3 & 1.0e-7 
  \\
  Case 2 biorep C & 40(*) & 1.0e-6
  \\
  Case 3 biorep A & 56.4 & 8.7e-7
  \\
  Case 3 biorep B & 72.8 & 7.4e-7 
  \\
  Case 3 biorep C & 64.9 & 4.3e-7 
  \\
  Case 4 biorep A & 60.4 & 8.8e-7 
  \\
  Case 4 biorep B & 61.7 & 7.9e-7 
  \\
  Case 4 biorep C & 57.6 & 8.1e-7 
  \\
  Case 5 biorep A & 78.7 & 5.7e-7 
  \\
  Case 5 biorep B & 76.7 & 5.8e-7 
  \\
  Case 5 biorep C & 80.8 & 1.8e-7 
  \\
  Case 6 biorep A & 47.8 & 2.8e-7 
  \\
  Case 6 biorep B & 49.4 & 4.1e-7 
  \\
  Case 6 biorep C & 52.9 & 4.4e-7 
  \\
  \botrule
  \end{tabular}%
  }
  {Shi et al. did not estimate purity for Case 2 biorep C. We chose 40\% purity, based on the other biological replicates from this case.}
\end{table*}

>>>>

\subsection{Estimation of the mutation profile}
Many aspects of genomic architecture can affect the somatic mutation rate at multiple scales \cite{Buisson2019}.
Here we focus on a small-scale feature, the trinucleotide context, which is known to strongly affect the prior probability of single-nucleotide mutation \cite{Nik-Zainal2012a,Alexandrov2015,Lee-Six2018}.
The trinucleotide context of a genomic site consists of the identity of the reference base and the 3' and 5' flanking bases.
There are six classes of base substitution: C$>$A, C$>$G, C$>$T, T$>$A, T$>$C, T$>$G (all referred to by the pyrimidine of the mutated Watson-Crick pair).
This results in a total of 32 ($4\times 2 \times 4$) reference contexts and 3 alternate bases per reference base.
%Folding the central base to the pyrimidines, there are two possible bases at the focal site, and there are four possible bases 3' and 5' of the focal site, yielding $2 \cdot 4 \cdot 4$ possible tri-nucleotide contexts $C$.
%At the focal site, a mutation $m$ can be to any of three alternate alleles.
Indexing by the $c=\{1 \dots 32\}$ contexts and by the $m = \{1 \dots 3\}$ alternate bases, we have 96 possible substitution types $S_{m,c}$.
Eq.~\ref{eqn:full_prior} is then
\begin{equation}
  \label{eqn:detailed_prior}
  \mathrm{p}(\mathrm{S}_{m,c}) = \mathrm{p}(m \mid C = c) \mathrm{p}(C = c \mid M)\frac{\mathrm{p}(M)}{\mathrm{p}(C = c)}.
\end{equation}
The first two terms on the right-hand side can be estimated from the observed mutation profile (Fig.~\ref{NAR-realsigfig}).
%Here $\mathrm{p}(\mathrm{S}_{m,c})$ represents probability that a substitution of type $\mathrm{S}_{m,c}$ will occur.

@@

\subsection{Estimation of the mutation rate}
The final piece of Eq. \ref{eqn:detailed_prior} is $p(M)$, the prior probability of mutation, which we specify as the per-base per-division mutation rate $\mu$.
In an exponentially growing and neutrally evolving tumor, branching process calculations \cite{Williams2018} show that the expected total number of mutations $\mathrm{M_{tot}}$ between two allele frequencies ($f_{min}$,$f_{max}$) is
\begin{equation}
  \label{eqn:mut_rate}
  \mathrm{M_{tot}}(f_{min},f_{max}) = N\frac{\mu}{\beta}\left(\frac{1}{f_{min}} - \frac{1}{f_{max}}\right).
\end{equation}
The number of bases $N$ is $3\cdot10^9$ for a whole genome and $3\cdot10^7$ for a whole exome.
The quantity $\mu/\beta$ is the effective mutation rate, where $\beta$ is the fraction of cell divisions that lead to two surviving lineages.
We make the simplifying assumption that there is no cell death ($\beta = 1$), so we somewhat over-estimate $\mu$.
We then estimate $\mu$ by counting observed high-confidence mutations between allele frequencies $f_{min}$ and $f_{max}$.
Sample contamination by normal cells can result in underestimation of tumor mutation allele frequencies.
To account for this, our implementation of BATCAVE takes as input an estimated sample purity $p_{ur}$.
All estimated allele frequencies are then multiplied by a factor of $1/p_{ur}$ before being used in Eq.~\ref{eqn:mut_rate}.
We set $f_{max}$ to be the largest allele frequency in $\mathrm{D}$, but we must choose $f_{min}$ conservatively, depending on sequencing depth.
In the R implementation of \batcave, $f_{min}$ and $p_{ur}$ are free parameters.
For this paper, we set $f_{min} = 0.05$, because we are working at high depth.
For our simulated data analyses, we set $p_{ur}=1$, and for our real data analyses, we set $p_{ur}$ to the estimated purity.

@@

An assumption of the \batcave algorithm is that the mutation profile of low-confidence mutations is similar to that of the high-confidence mutations from which the prior is inferred.
To test this assumption, \texttt{batcaver} performs a statistical hypothesis test comparing these two mutation profiles \cite{Plunkett2019}.
If the two profiles differ at a significance threshold of $\alpha=0.05$, \texttt{batcaver} issues a warning and outputs the profiles.
%The user can then assess them and follow-up on any biologically interesting differences.

@@

\subsection{Real data}
We analyzed two real data sets, one from an acute myeloid leukemia (AML)~\cite{Griffith2015} and one from a multi-region sequencing experiment in breast cancer~\cite{Shi2018}.
We downloaded the normal and primary whole-genome AML tumor bam files from dbGaP accession number phs000159.v8.p4.
Griffith et al.\ generated a platinum set of variant calls for this tumor~\cite{Griffith2015}, which we used for our true positive dataset.
We downloaded the normal and tumor whole-exome breast cancer bam files from NCBI Sequence Read Archive accession SRP070662.
Griffith et al.\ estimated the purity of their primary sample to be 90.7\%, and we used this value for tumor purity in \texttt{batcaver}.
Shi et al.\ generated a gold set of variant calls for each tumor region sequenced~\cite{Shi2018}, which we used for our true positive dataset.
For these multi-region data, we analyzed the three biological replicates from each of six tumors (Table~\ref{table:01}), running \batcave separately on each of the eighteen samples, and we combined results to generate precision-recall curves.
Shi et al.\ estimated sample purities of between 26\% and 80\%, and we used these estimates in \texttt{batcaver}.
We called variants using Mutect 1.1.7 as in our simulations, except that both these data sets were originally aligned to GRCh37, so we used that reference.

@@

\begin{table*}[b]
  \tableparts{%
  \caption{Variant calling metrics for all data sets.}
  \label{table:01}%
  }{%
  \begin{tabular}{lllllllllll}
  \toprule
  Scenario & Mutation profile & $\mu$ & \multicolumn{2}{c}{AUROC} & \multicolumn{2}{c}{AUPRC} & \multicolumn{2}{c}{ICI} 
  \\
  & & (estimated) & MuTect & \batcave & MuTect & \batcave & MuTect & \batcave
  \\
  \colrule
  100X whole genome & Concentrated & 3.6e-7 & .987 & .993 & .972 & .975 & .117 & .287
  \\
  100X whole genome & Intermediate & 3.2e-7 & .987 & .989 & .972 & .973 & .118 & .214
  \\
  100X whole genome & Diffuse & 3.2e-7 & .988 & .989 & .971 & .973 & .120 & .219
  \\
  500X whole exome & Concentrated & 3.6e-7 & .848 & .929 & .674 & .758 & .138 & .109
  \\
  500X whole exome & Intermediate & 3.6e-7 & .847 & .881 & .677 & .706 & .108 & .112 
  \\
  500X whole exome & Diffuse & 3.6e-7 & .850 & .873 & .676 & .698 & .105 & .116
  \\
  real AML \cite{Griffith2015} & Actual & 3.6e-8 & -- & -- & .996 & .988 & -- & --
  \\
  real breast \cite{Shi2018} & Actual & 6.6e-7 & -- & -- & .972 & .968 & -- & --
  \\
  \botrule
  \end{tabular}%
  }
  {$\mu$ = per-base mutation rate, AUROC/AUPRC = Area Under Receiver Operating Characteristic / Precision-Recall Curve, ICI = Integrated Calibration Index. Smaller values of ICI are superior.}
 \end{table*}

@@

Griffith et al.\ sequenced the whole genome of an acute myeloid leukemia (AML) primary tumor to a depth of $>$360X and used targeted sequencing to validate nearly 200,000 mutations~\cite{Griffith2015}.
We estimated a per-base mutation rate for this tumor of $3.6\times10^{-8}$, which is consistent with previous estimates of AML mutation rates \cite{Griffith2015,Williams2018}.
For this tumor, the mutation profiles of high- and low-confidence mutations differ ($p \sim 10^{-12}$).
The low-confidence mutation profile contains additional spikes of mutations corresponding to five substitution types (Fig.~\ref{fig:AML_profiles}).
Nevertheless, for both MuTect and \batcave, the precision-recall curve is almost perfect for the validated variants (.988 \& .996 area under the curve) (Fig.~\ref{NAR-wes_fig}E and Table~\ref{table:01}).

Shi et al.\ performed multi-region whole exome sequencing on six individual breast tumors to a mean target sequencing depth of 160X and validated all variants identified by three different variant calling pipelines~\cite{Shi2018}.
%We downloaded aligned reads for this tumor, and called variants with MuTect 1.1.7 as described in Materials \& Methods.
We estimated an average per-base mutation rate for these tumor regions of $6.6\times10^{-7}$, which is consistent with observed mutation rates for breast cancers \cite{Alexandrov2019} and with the low number of validated somatic mutations.
For the validated variants, MuTect and \batcave yielded almost identical precision-recall curves (Fig.~\ref{NAR-wes_fig}F and Table~\ref{table:01})

@@

Following MuTect \cite{Cibulskis2013}, \batcave assumes a uniform prior on the variant allele frequency.
In general, low-frequency variants are expected to be more common than high-frequency variants.
Nevertheless, the uniform frequency prior is appropriate when the goal is to make the best call possible at each potential variant site.
By favoring low-frequency and thus typically low-evidence variants, a nonuniform prior would increase the false positive rate.
Note however, that if the goal were not to best identify individual variants, but rather to best estimate the distribution of variant allele frequencies within the tumor, then a nonuniform frequency prior would be appropriate~\cite{Nielsen2012}.

To estimate the tumor mutation rate, \batcave uses a model of the distribution of variant allele frequencies  generated during exponential growth (Eq.~\ref{eqn:mut_rate}).
Mutations that change copy number might distort the empirical allele frequency distribution, biasing the estimate.
But substantially biasing the estimate would require copy number changes in a large number of genomic regions.
Nevertheless, a potential extension of the \batcave algorithm would be to incorporate external copy number calls in order to adjust allele frequencies before estimating the mutation rate.

Sequencing multiple regions of the same tumor is of growing interest for understanding tumor heterogeneity and evolution \cite{McGranahan2017}.
In fact, the breast cancer data we analyze came from a multi-region study~\cite{Shi2018}.
We called variants independently across samples, because MuTect only considers a single sample at a time.
But calling variants jointly across samples could substantially increase sensitivity.
In the future, the \batcave algorithm could be integrated into a multi-sample caller such as MultiSNV~\cite{Josephidou2015}.
In that case, an optimal implementation would likely exploit the relationship between mutational priors in related samples.

@@

An  implicit assumption of \batcave is that the mutational process does not change between high- and low-confidence variants, implying that the mutational profile of the tumor is temporally constant.
Recent studies have found differences in mutational profiles among variants of different allelic frequencies~\cite{Rubanova2018a}, and although in general those differences are relatively small, they can be significant in some cases.
Our \texttt{batcaver} software warns the user if the high- and low-confidence mutational profiles are statistically different.
It also outputs those profiles, so the user can assess whether the difference will substantially affect their results.
A potential extension of the \batcave algorithm is to process potential variants in order of descending allelic frequency and to update the estimated mutational prior as the algorithm proceeds.
This approach might increase sensitivity to low-frequency variants generated by recently-arisen mutational processes, at the cost of potentially increasing sensitivity to patterns of sequencing error.

@@

\begin{table*}[h]
  \tableparts{%
  \caption{Sample summary for Shi et al. (2018)}
  \label{table:01}%
  }{%
  \begin{tabular}{lll}
  \toprule
  Sample & Purity estimate (\%) & Mutation rate estimate 
  \\
  \colrule
  Case 1 biorep A & 53.8 & 9.3e-7 
  \\
  Case 1 biorep B & 46.3 & 8.4e-7 
  \\
  Case 1 biorep C & 26.0 & 1.0e-6 
  \\
  Case 2 biorep A & 40.0 & 1.1e-6 
  \\
  Case 2 biorep B & 32.3 & 1.0e-7 
  \\
  Case 2 biorep C & 40(*) & 1.0e-6
  \\
  Case 3 biorep A & 56.4 & 8.7e-7
  \\
  Case 3 biorep B & 72.8 & 7.4e-7 
  \\
  Case 3 biorep C & 64.9 & 4.3e-7 
  \\
  Case 4 biorep A & 60.4 & 8.8e-7 
  \\
  Case 4 biorep B & 61.7 & 7.9e-7 
  \\
  Case 4 biorep C & 57.6 & 8.1e-7 
  \\
  Case 5 biorep A & 78.7 & 5.7e-7 
  \\
  Case 5 biorep B & 76.7 & 5.8e-7 
  \\
  Case 5 biorep C & 80.8 & 1.8e-7 
  \\
  Case 6 biorep A & 47.8 & 2.8e-7 
  \\
  Case 6 biorep B & 49.4 & 4.1e-7 
  \\
  Case 6 biorep C & 52.9 & 4.4e-7 
  \\
  \botrule
  \end{tabular}%
  }
  {Shi et al. did not estimate purity for Case 2 biorep C. We chose 40\% purity, based on the other biological replicates from this case.}
\end{table*}
